Towards Contract Modules for the Tezos Blockchain

### 2021-05-25 papers/contract-modules/fmbc2021/fmbc-main.tex

>>>>

The basic idea of our advanced checking, namely precondition checking, is derived from Java Modeling Language (JML)\cite{Leavens2006DesignBC, 101007}, where the behavior of program components is described as an executable contract between Java programs and their clients. This executable contract specifies preconditions that must be satisfied by clients and postconditions that are guaranteed by the program. A precondition supplied with a client call must be satisfied before a function defined by the program is called, and the program guarantees that the postconditions are satisfied in return after the call. The original use of such preconditions and postconditions dates back to Hoare's paper on formal verification \cite{101145}. The executable contracts are written as program code in the programming language. In our approach, the safe contract module in Ocaml plays a role as an executable contract. Several applications are based on JML \cite{Tran2017, keY}. Ahrendt et al. \cite{keY} propose a framework called The KeY for deductive software verification. The module specifies preconditions and then verifies where a user call satisfies those preconditions. Symbolic execution plays an important role in precondition checking in our method. A contract is verified against its specification in the contract module by symbolic execution. Hentschel et al. \cite{Hentschel} proposed the symbolic execution debugger (SED) platform based on the KeY framework. The platform SED has a static symbolic execution engine for sequential programs.
